### 2014-04-15 doc/uist14/iteration3.tex
Iteration 3: Description of orientation system
* Added \achal macro for comment
* Revised most of iteration 3

\section{Iteration 3: Head motion for disambiguation}
\label{sec:iteration-3:-head}

Though our {\em Valued IR} system is already performing well (with 3.71 seconds on average in a relative dense environment), we are only using head-orientation information during the {\em coarse selection} stage. In the {\em fine selection} part, we rely on the near-eye display. This has one fundamental problem -- we are projecting a high dimension distribution to a 1-dimension list. Therefore, it motivates us to explore using head orientation also during the {\em fine selection} stage.

@@

The sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of users' head. However, such absolute orientation cannot be directly used in any indoor environment because the user might change his location. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and sensors on Glass.

Before we describe how this new technique works. The relative orientation information -- {\em adjacent map} -- has to be learned before we can use it. Such a learning process can either be performed a prior, or through demonstration. \ben{need better elaboration here}.

In this hybrid approach, in additional to use IR to reduce the chance of disambiguation and prepare a better list, the IR information helps us identify a base point. When the user wants to use his head-motion for disambiguation, he will put his finger on the touchpad to enter a quasi-mode. Such a gesture comes from a real-world metaphor that people tend to adjust their glasses for a closer inspection. In such quasi-mode, we monitor the changes of his head orientation, and infer the intended next targets according to some algorithm \ben{haven't described yet}.

\ben{We then need evaluation results here, quantitative and qualitative.}

>>>>

\section{Iteration 3: Head motion for disambiguation}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Though our {\em Valued IR} system already performs well (with 3.71 seconds on average in a relative dense environment), head-orientation information is only used during the {\em coarse selection} stage. In the {\em fine selection} phase, we rely solely on the near-eye display. This has two problems: First, we are projecting a high dimension distribution to a 1-dimension list. Second, this requires the user to switch their focus back and forth between the physical world and the display. This issue motivated us to design an approach that also utilizes orientation information during the {\em fine selection} stage, so that there would be a more direct mapping between the user's gestures and target selection.

@@

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of users' head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change his location \achal{Should we use gender neutral language?}. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and sensors on Glass.

There are two phases to this technique: learning the relative orientations and intelligently suggesting targets during disambiguation.

In the first stage, the user orients his head towards each device, and the system saves the absolute orientations of each device. Once the user has added all devices, these orientations are saved for future use. It is still possible to add new devices at any point without running the entire calibration step, as the system will simply store the absolute orientation of the new device.

During the second stage, when the user wants to use his head-motion for disambiguation, he will put his finger on the touchpad to enter a quasi-mode.  This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.

In this mode, only one device has a solid indicator light on at a time. The user can then tilt in the direction of the device he wishes to switch to. We calculate the direction of movement using a low-passed history of orientations, and look for devices that lay in that direction. Once a new device is selected, the frame of reference changes, and the user can repeat the process. Note that in reality, this is a completely smooth operation: it is possible to switch between multiple devices in one continuous motion. This is achieved by automatically adjusting the frame of reference to the currently lit device, but also creating a ``sticky" threshold so that the user is not constantly jumping between devices.

\achal{Not sure if there should be a conclusion of some sort here.}

\subsection{Evaluation}
\ben{We then need evaluation results here, quantitative and qualitative.}
